Histo of ____

### 2017-07-13 msk2.rmd
deleted old

-  Gout 
-  Septic arthropathies
-  Trauma
-  Osteoarthritis
-  Psoriatic arthritis

>>>>

-  Gout: first MTP joint
-  Septic arthritis: one large joint
-  Trauma
-  Osteoarthritis: knee/hips (weight bearing)
-  RA: little joints
-  Psoriatic arthritis
-  Bleeding into the joints: haemophilia

Other Qs to ask

-  Skin conditions: psoriatic
-  Fever/inf: septic arthritis
-
